---
title: "HerbPt1 16S Figures"
output: html_notebook
---

```{r}
require(phyloseq)
require(tidyverse)
require(phyloseq)
require(reshape2)
require(dplyr)
require(ggplot2)
```

Load data
```{r}
ps_dmn <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/DMN_ests_16S.Rdata")
sample_data(ps_dmn)$Herbicide <- factor(sample_data(ps_dmn)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
sample_data(ps_dmn)$herb_time<-paste(sample_data(ps_dmn)$Herbicide, sample_data(ps_dmn)$Time, sep = "_")

ps_rare <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_rare_16S.Rdata")
sample_data(ps_rare)$Herbicide <- factor(sample_data(ps_rare)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
sample_data(ps_rare)$herb_time<-paste(sample_data(ps_rare)$Herbicide, sample_data(ps_rare)$Time, sep = "_")

ps_trans <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_hel_trans_16S.Rdata")
sample_data(ps_trans)$Herbicide <- factor(sample_data(ps_trans)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
sample_data(ps_trans)$herb_time<-paste(sample_data(ps_trans)$Herbicide, sample_data(ps_trans)$Time, sep = "_")
```

create alphadiversity tables
```{r}
alpha_div <- estimate_richness(physeq = ps_rare, measures = c("Observed", "Shannon", "Chao1"))
#pull out metadata and concatonate with alpha diversity metrics
md<-data.frame(sample_data(ps_rare))
alpha_div_md <- rownames_to_column(alpha_div, "Barcode_ID_G") %>% full_join(md) 
alpha_div_md$Herbicide <- factor(alpha_div_md$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
```

Shannon Div plots - no significant differences among herbicide treatments at any of the three time points
```{r}
ggplot(data = alpha_div_md, aes(Herbicide, Shannon, color= Herbicide)) + facet_grid(. ~ Time) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1) )

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_Shannon.pdf")

aov_t1<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T1",])
plot(aov_t1$residuals)
summary(aov_t1)

aov_t2<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T2",])
plot(aov_t2$residuals)
summary(aov_t2)

aov_t3<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T3",])
plot(aov_t3$residuals)
summary(aov_t3)
```

ordinations and adonis testing with three separate objects (i.e., dmn, rarefied, transformed). Rare taxa are removed from rarefied and transfomred to sucessfully ordinate. At this point, the transformed data will not ordinate. 
```{r}
ord_dmn<-ordinate(physeq = ps_dmn, method = "NMDS", distance = "bray", k=3, trymax= 300, maxit=1000)

ps_rare_sub<-prune_taxa(taxa_sums(ps_rare) > 2, ps_rare)
ord_rare<-ordinate(physeq = ps_rare_sub, method = "NMDS", distance = "bray", k=3, trymax= 300, maxit=1000)

ps_trans_sub<-prune_taxa(taxa_sums(ps_trans) > 0.05, ps_trans)
ord_transformed<-ordinate(physeq = ps_trans_sub, method = "NMDS", distance = "bray", trymax= 300, maxit=1000)
```

Adonis testing of herbicide treatments by time point
```{r}
ps_adonis<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
  print(anova(vegan::betadisper(physeq_dist, md_tab$Herbicide)))
  vegan::adonis(physeq_dist ~ Herbicide * Time, data = md_tab, permutations = 1000)
}
```

```{r}
ps_adonis(ps_rare_sub)
#ps_adonis(ps_trans_sub)
ps_adonis(ps_dmn)
```

Ordination plots DMN
```{r}
ord_t1_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T1"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T1_dmn<-ggordiplots::gg_ordiplot(ord = ord_t1_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_dmn$plot + theme_classic()

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T1.pdf")

ord_t2_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T2"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T2_dmn<-ggordiplots::gg_ordiplot(ord = ord_t2_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T2")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T2_dmn$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T2.pdf")


ord_t3_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T3"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T3_dmn<-ggordiplots::gg_ordiplot(ord = ord_t3_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T3")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T3_dmn$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T3.pdf")
```

Ordination plots rarefied
```{r}
ord_t1_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T1"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T1_rare<-ggordiplots::gg_ordiplot(ord = ord_t1_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_rare$plot + theme_classic()

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T1.pdf")

ord_t2_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T2"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T2_rare<-ggordiplots::gg_ordiplot(ord = ord_t2_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T2")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T2_rare$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T2.pdf")


ord_t3_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T3"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T3_rare<-ggordiplots::gg_ordiplot(ord = ord_t3_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T3")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T3_rare$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T3.pdf")
```


Pairwise adonis testing
```{r}


ps_pairwiseadonis<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
pairwiseAdonis::pairwise.adonis(x = physeq_dist, factors = md_tab$Herbicide, p.adjust.m = "none", perm = 1000)
}

ps_t1<-subset_samples(ps_rare_sub, Time == "T1")
ps_t1<-prune_taxa(taxa_sums(ps_t1) > 2, ps_t1)

ps_t2<-subset_samples(ps_rare_sub, Time == "T2")
ps_t2<-prune_taxa(taxa_sums(ps_t2) > 2, ps_t2)

ps_t3<-subset_samples(ps_rare_sub, Time == "T3")
ps_t3<-prune_taxa(taxa_sums(ps_t3) > 2, ps_t3)


ps_pairwiseadonis(ps_t1)
ps_pairwiseadonis(ps_t2)
ps_pairwiseadonis(ps_t3)


```


box and whisker plots of distance 
within group distances
```{r}
library(micrUBIfuns)
beta_boxplot(physeq = subset_samples(ps_rare, Time=="T1"), method = "bray", group = "Herbicide")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T1_rare_withingroup_beta.pdf")
beta_boxplot(physeq = subset_samples(ps_rare, Time=="T2"), method = "bray", group = "Herbicide")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T2_rare_withingroup_beta.pdf")
beta_boxplot(physeq = subset_samples(ps_rare, Time=="T3"), method = "bray", group = "Herbicide")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T3_rare_withingroup_beta.pdf")
```

treatment to control 
```{r}
plotDistances = function(p, m, s, d) {

  # calc distances
  wu = phyloseq::distance(p, m)
  wu.m = melt(as.matrix(wu))
  
  # remove self-comparisons
  wu.m = wu.m %>%
    filter(as.character(Var1) != as.character(Var2)) %>%
    mutate_if(is.factor,as.character)
  
  # get sample data (S4 error OK and expected)
  sd = data.frame(sample_data(p)) %>%
    select(s, d) %>%
    mutate_if(is.factor,as.character)
  sd$Herbicide <- factor(sd$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
  
  # combined distances with sample data
  colnames(sd) = c("Var1", "Type1")
  wu.sd = left_join(wu.m, sd, by = "Var1")
  
  colnames(sd) = c("Var2", "Type2")
  wu.sd = left_join(wu.sd, sd, by = "Var2")
  
  #remove this line to plot all comparisons. 
  wu.sd = wu.sd %>% filter(Type1 == "Hand" | Type1 == "Non-Treated")
  
  # plot
  ggplot(wu.sd, aes(x = Type2, y = value)) +
    theme_bw() +
    geom_point() +
    geom_boxplot(aes(color = ifelse(Type1 == Type2, "red", "black"))) +
    scale_color_identity() +
    facet_wrap(~ Type1, scales = "free_x") +
    theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
    ggtitle(paste0("Distance Metric = ", m))
  
}
```


```{r}
a<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T1"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
a <- a + ggtitle("Time 1 Bray-Curtis Dissimlarities")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T1_rare_allgroup_beta.pdf")
b<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T2"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
b <-b + ggtitle("Time 2 Bray-Curtis Dissimlarities")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T2_rare_allgroup_beta.pdf")
c<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T3"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
c<- c + ggtitle("Time 3 Bray-Curtis Dissimlarities")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T3_rare_allgroup_beta.pdf")

library(ggpubr)
ggarrange(a, b, c, ncol = 1)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_rare_allgroup_beta.pdf", width = 7, height = 10)
```
Taxon abundance bar plot

```{r}
#create super long color vector
col_vector <- c("#000000", "#FFFF00", "#1CE6FF", "#FF34FF", "#FF4A46", "#008941", "#006FA6", "#A30059",
        "#FFDBE5", "#7A4900", "#0000A6", "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87",
        "#5A0007", "#809693", "#FEFFE6", "#1B4400", "#4FC601", "#3B5DFF", "#4A3B53", "#FF2F80",
        "#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92", "#FF90C9", "#B903AA", "#D16100",
        "#DDEFFF", "#000035", "#7B4F4B", "#A1C299", "#300018", "#0AA6D8", "#013349", "#00846F",
        "#372101", "#FFB500", "#C2FFED", "#A079BF", "#CC0744", "#C0B9B2", "#C2FF99", "#001E09",
        "#00489C", "#6F0062", "#0CBD66", "#EEC3FF", "#456D75", "#B77B68", "#7A87A1", "#788D66",
        "#885578", "#FAD09F", "#FF8A9A", "#D157A0", "#BEC459", "#456648", "#0086ED", "#886F4C",
        
        "#34362D", "#B4A8BD", "#00A6AA", "#452C2C", "#636375", "#A3C8C9", "#FF913F", "#938A81",
        "#575329", "#00FECF", "#B05B6F", "#8CD0FF", "#3B9700", "#04F757", "#C8A1A1", "#1E6E00",
        "#7900D7", "#A77500", "#6367A9", "#A05837", "#6B002C", "#772600", "#D790FF", "#9B9700",
        "#549E79", "#FFF69F", "#201625", "#72418F", "#BC23FF", "#99ADC0", "#3A2465", "#922329",
        "#5B4534", "#FDE8DC", "#404E55", "#0089A3", "#CB7E98", "#A4E804", "#324E72", "#6A3A4C",
        "#83AB58", "#001C1E", "#D1F7CE", "#004B28", "#C8D0F6", "#A3A489", "#806C66", "#222800",
        "#BF5650", "#E83000", "#66796D", "#DA007C", "#FF1A59", "#8ADBB4", "#1E0200", "#5B4E51",
        "#C895C5", "#320033", "#FF6832", "#66E1D3", "#CFCDAC", "#D0AC94", "#7ED379", "#012C58",
        
        "#7A7BFF", "#D68E01", "#353339", "#78AFA1", "#FEB2C6", "#75797C", "#837393", "#943A4D",
        "#B5F4FF", "#D2DCD5", "#9556BD", "#6A714A", "#001325", "#02525F", "#0AA3F7", "#E98176",
        "#DBD5DD", "#5EBCD1", "#3D4F44", "#7E6405", "#02684E", "#962B75", "#8D8546", "#9695C5",
        "#E773CE", "#D86A78", "#3E89BE", "#CA834E", "#518A87", "#5B113C", "#55813B", "#E704C4",
        "#00005F", "#A97399", "#4B8160", "#59738A", "#FF5DA7", "#F7C9BF", "#643127", "#513A01",
        "#6B94AA", "#51A058", "#A45B02", "#1D1702", "#E20027", "#E7AB63", "#4C6001", "#9C6966",
        "#64547B", "#97979E", "#006A66", "#391406", "#F4D749", "#0045D2", "#006C31", "#DDB6D0",
        "#7C6571", "#9FB2A4", "#00D891", "#15A08A", "#BC65E9", "#FFFFFE", "#C6DC99", "#203B3C",

        "#671190", "#6B3A64", "#F5E1FF", "#FFA0F2", "#CCAA35", "#374527", "#8BB400", "#797868",
        "#C6005A", "#3B000A", "#C86240", "#29607C", "#402334", "#7D5A44", "#CCB87C", "#B88183",
        "#AA5199", "#B5D6C3", "#A38469", "#9F94F0", "#A74571", "#B894A6", "#71BB8C", "#00B433",
        "#789EC9", "#6D80BA", "#953F00", "#5EFF03", "#E4FFFC", "#1BE177", "#BCB1E5", "#76912F",
        "#003109", "#0060CD", "#D20096", "#895563", "#29201D", "#5B3213", "#A76F42", "#89412E",
        "#1A3A2A", "#494B5A", "#A88C85", "#F4ABAA", "#A3F3AB", "#00C6C8", "#EA8B66", "#958A9F",
        "#BDC9D2", "#9FA064", "#BE4700", "#658188", "#83A485", "#453C23", "#47675D", "#3A3F00",
        "#061203", "#DFFB71", "#868E7E", "#98D058", "#6C8F7D", "#D7BFC2", "#3C3E6E", "#D83D66",

        "#2F5D9B", "#6C5E46", "#D25B88", "#5B656C", "#00B57F", "#545C46", "#866097", "#365D25",
        "#252F99", "#00CCFF", "#674E60", "#FC009C", "#92896B")
```

```{r}
phylumGlommed <- tax_glom(ps_rare, "Phylum")

#t1
phylumGlommed_herb_t1 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T1"), group = "Herbicide")
phylumGlommed_herb_t1 <- transform_sample_counts(phylumGlommed_herb_t1, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t1)$Herbicide <- factor(sample_data(phylumGlommed_herb_t1)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t1, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_Taxon_barplot_t1.pdf")

#t2
phylumGlommed_herb_t2 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T2"), group = "Herbicide")
phylumGlommed_herb_t2 <- transform_sample_counts(phylumGlommed_herb_t2, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t2)$Herbicide <- factor(sample_data(phylumGlommed_herb_t2)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t2, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_Pt1/Figures/16S_Taxon_barplot_t2.pdf")

#t3
phylumGlommed_herb_t3 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T3"), group = "Herbicide")
phylumGlommed_herb_t3 <- transform_sample_counts(phylumGlommed_herb_t3, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t3)$Herbicide <- factor(sample_data(phylumGlommed_herb_t3)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t3, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_Pt1/Figures/16S_Taxon_barplot_t3.pdf")
```
Combined herbicide and time bar plot for exploration
```{r}
sample_data(ps_rare)$herb_time<-paste(sample_data(ps_rare)$Herbicide, sample_data(ps_rare)$Time, sep = "_")
ps_rare_for_barplot <- prune_taxa(taxa_sums(ps_rare) > 50, ps_rare)
plot_bar(ps_rare_for_barplot, x= "herb_time", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_BarPlot_Herbicide_Time.pdf", width = 20, height = 11)
```


Linear modeling of abundant taxa
```{r}

Tax_glom_Subset <- function (physeq, y = "taxLevel", nreturns = "Number of returns"){
   ps_1<- tax_glom(ps_rare_sub, taxrank = y )
    myTaxa <- names(sort(taxa_sums(ps_1), decreasing = TRUE)[1:nreturns])
       ps_1_sub <- prune_taxa(myTaxa, ps_1)
  return(ps_1_sub)
}

ps_rare_family_top25<-Tax_glom_Subset(physeq = ps_rare, nreturns = 25, y = "Family")

#explore top 25 taxa with plot bar
plot_bar(ps_rare_family_top25, x= "herb_time", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")


#write function to wrangle data prior to anova

abund_aov_wrangle <- function (physeq, y = "Tax_Level"){
  tax<-tax_table(physeq)[,y]
   meta<-data.frame(sample_data(physeq))
  counts<-data.frame(otu_table(physeq))
  rownames(counts) <- tax[,1]
  counts<-data.frame(t(counts))
   counts$Time <- meta$Time 
   counts$Herbicide <- meta$Herbicide 
  counts$Herb_time <- meta$herb_time 
  return(counts)
}            

test<-abund_aov_wrangle(ps_rare_family_top25, y = "Family")

mod_abund<-function(count_tab, IV = "Groups to be tested") {
   for(j in 1:length(unique(count_tab[,"Herbicide"]))){
         data <- count_tab %>% filter(Herbicide == unique(count_tab$Herbicide)[j])
           #change this to the number of returns from the tax_glom_subset function
   for (i in 1:25) { 
            mod <- aov(unlist(data[i]) ~ matrix(data[,IV])) 
            #sanity check
            print(c(j, i))
   if(summary(mod)[[1]][["Pr(>F)"]][1] <= 0.05) {
            print(summary(mod))
         print(boxplot(unlist(data[i]) ~ unlist(data[IV]), main =paste(names(data[i]), as.character(unique(count_tab[,"Herbicide"]))[j]), xlab= "Time", ylab="Abundance") )
           }
         }
      }
    }


mod_abund(test, IV = "Time")
```
