---
title: "HerbPt1 16S Figures"
output: html_notebook
---

```{r}
require(phyloseq)
require(tidyverse)
require(reshape2)
require(dplyr)
require(ggplot2)
require(vegan)
```

Load data order, factors, and create a mode (chemical, hand, non-treated) column.
```{r}
ps_dmn <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/DMN_ests_16S.Rdata")
sample_data(ps_dmn)$Herbicide <- factor(sample_data(ps_dmn)$Herbicide, levels = c("Aatrex", "Clarity", "Hand","Non-Treated","Roundup Powermax"))
sample_data(ps_dmn)$herb_time<-paste(sample_data(ps_dmn)$Herbicide, sample_data(ps_dmn)$Time, sep = "_")

#regroup all chemical treatments together and rerun betadiv calcs within group. 
sample_data(ps_dmn)$Mode<-sample_data(ps_dmn)$Herbicide

index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Chemical", "Chemical", "Chemical", "Hand", "Non-Treated")

sample_data(ps_dmn)$Mode<- as.factor(values[match(sample_data(ps_dmn)$Mode, index)])


index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Dicamba", "Glyphosate", "Atrazine-Mesotrione", "Handweeded", "Non-Treated")

sample_data(ps_dmn)$Herbicide <- as.factor(values[match(sample_data(ps_dmn)$Herbicide, index)])



ps_rare <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_rare_16S.Rdata")
sample_data(ps_rare)$Herbicide <- factor(sample_data(ps_rare)$Herbicide, levels = c("Aatrex", "Clarity", "Hand","Non-Treated","Roundup Powermax"))
sample_data(ps_rare)$herb_time<-paste(sample_data(ps_rare)$Herbicide, sample_data(ps_rare)$Time, sep = "_")


#regroup all chemical treatments together and rerun betadiv calcs within group. 
sample_data(ps_rare)$Mode<-sample_data(ps_rare)$Herbicide

index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Chemical", "Chemical", "Chemical", "Hand", "Non-Treated")

sample_data(ps_rare)$Mode<- as.factor(values[match(sample_data(ps_rare)$Mode, index)])

index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Dicamba", "Glyphosate", "Atrazine-Mesotrione", "Handweeded", "Non-Treated")

sample_data(ps_rare)$Herbicide <- as.factor(values[match(sample_data(ps_rare)$Herbicide, index)])

ps_trans <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_hel_trans_16S.Rdata")
sample_data(ps_trans)$Herbicide <- factor(sample_data(ps_trans)$Herbicide, levels = c("Aatrex", "Clarity", "Hand","Non-Treated","Roundup Powermax"))
sample_data(ps_trans)$herb_time<-paste(sample_data(ps_trans)$Herbicide, sample_data(ps_trans)$Time, sep = "_")

#regroup all chemical treatments together and rerun betadiv calcs within group. 
sample_data(ps_trans)$Mode<-sample_data(ps_trans)$Herbicide

index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Chemical", "Chemical", "Chemical", "Hand", "Non-Treated")

sample_data(ps_trans)$Mode<- as.factor(values[match(sample_data(ps_trans)$Mode, index)])

index <- c("Clarity", "Roundup Powermax", "Aatrex", "Hand", "Non-Treated")
values <- c("Dicamba", "Glyphosate", "Atrazine-Mesotrione", "Handweeded", "Non-Treated")

sample_data(ps_trans)$Herbicide <- as.factor(values[match(sample_data(ps_trans)$Herbicide, index)])
```



create alpha diversity tables
```{r}
alpha_div <- estimate_richness(physeq = ps_rare, measures = c("Observed", "Shannon", "Chao1"))
#pull out metadata and concatonate with alpha diversity metrics
md<-data.frame(sample_data(ps_rare))
alpha_div_md <- rownames_to_column(alpha_div, "Barcode_ID_G") %>% full_join(md) 

alpha_div_md$Herbicide <- factor(alpha_div_md$Herbicide, levels = c("Non-Treated", "Handweeded", "Atrazine-Mesotrione", "Dicamba", "Glyphosate"))
```

Shannon Div plots - no significant differences among herbicide treatments at any of the three time points
```{r}
ggplot(data = alpha_div_md, aes(Herbicide, Shannon, color= Herbicide)) + facet_grid(. ~ Time) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1) )

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_Shannon.pdf")

aov_t1<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T1",])
plot(aov_t1$residuals)
summary(aov_t1)

aov_t2<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T2",])
plot(aov_t2$residuals)
summary(aov_t2)

aov_t3<-aov(Chao1 ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T3",])
plot(aov_t3$residuals)
summary(aov_t3)
```

remove outliers and rare reads with less than 2 total reads
```{r}
ps_dmn <-  subset_samples(ps_dmn, sample_names(ps_rare) != "G166SG")

ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G166SG")
ps_rare_sub<-prune_taxa(taxa_sums(ps_rare) > 2, ps_rare)

ps_trans_sub<-prune_taxa(taxa_sums(ps_trans) > 0.05, ps_trans)

```


ordinations and adonis testing with three separate objects (i.e., dmn, rarefied, transformed). Rare taxa are removed from rarefied and transfomred to sucessfully ordinate. At this point, the transformed data will not ordinate. 
```{r}

ord_dmn<-ordinate(physeq = ps_dmn, method = "NMDS", distance = "bray", k=3, trymax= 300, maxit=1000)


ord_rare<-ordinate(physeq = ps_rare_sub, method = "NMDS", distance = "bray", k=3, trymax= 300, maxit=1000)
full_ord_rare<-ggordiplots::gg_ordiplot(ord = ord_rare, groups = data.frame(sample_data(ps_rare))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
full_ord_rare$plot + theme_classic()

ord_transformed<-ordinate(physeq = ps_trans_sub, method = "NMDS", distance = "bray", trymax= 300, maxit=1000)
```

Adonis testing of herbicide treatments by time point
```{r}
ps_adonis<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
  print(anova(vegan::betadisper(physeq_dist, md_tab$Herbicide)))
  vegan::adonis2(physeq_dist ~ Herbicide * Time + Total_Weed_Veg , data = md_tab, permutations = 1000)
}
```

remove one sample with no vegetation measurement. 
```{r}
ps_rare_sub_57<-subset_samples(ps_rare_sub, sample_names(ps_rare_sub) != "G065SG")
ps_adonis(ps_rare_sub_57)

ps_dmn_57<-subset_samples(ps_dmn, sample_names(ps_dmn) != "G065SG")
ps_adonis(ps_dmn_57)
```


effect of herbicide treatment at each timepoint as per significant interaction term.
```{r}

ps_adonis_split_by_timepoint<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
  print(anova(vegan::betadisper(physeq_dist, md_tab$Herbicide)))
  vegan::adonis2(physeq_dist ~ Herbicide + Total_Weed_Veg , data = md_tab, permutations = 1000)
}


#rarefied
ps_rare_sub_57_T1<-subset_samples(ps_rare_sub_57, Time=="T1")
ps_adonis_split_by_timepoint(ps_rare_sub_57_T1)

ps_rare_sub_57_T2<-subset_samples(ps_rare_sub_57, Time=="T2")
ps_adonis_split_by_timepoint(ps_rare_sub_57_T2)

ps_rare_sub_57_T3<-subset_samples(ps_rare_sub_57, Time=="T3")
ps_adonis_split_by_timepoint(ps_rare_sub_57_T3)

#DMN
ps_dmn_sub_57_T1<-subset_samples(ps_dmn_57, Time=="T1")
ps_adonis_split_by_timepoint(ps_dmn_sub_57_T1)

ps_dmn_sub_57_T2<-subset_samples(ps_dmn_57, Time=="T2")
ps_adonis_split_by_timepoint(ps_dmn_sub_57_T2)

ps_dmn_sub_57_T3<-subset_samples(ps_dmn_57, Time=="T3")
ps_adonis_split_by_timepoint(ps_dmn_sub_57_T3)
```

Ordination plots DMN
```{r}
ord_t1_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T1"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T1_dmn<-ggordiplots::gg_ordiplot(ord = ord_t1_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_dmn$plot + theme_classic() + xlim(-0.3, 0.3) + ylim(-0.3, 0.3)

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T1.pdf")

ord_t2_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T2"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T2_dmn<-ggordiplots::gg_ordiplot(ord = ord_t2_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T2")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
T2_dmn$plot + theme_classic()+ xlim(-0.3, 0.3) + ylim(-0.3, 0.3)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T2.pdf")


ord_t3_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T3"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T3_dmn<-ggordiplots::gg_ordiplot(ord = ord_t3_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T3")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1) 
T3_dmn$plot + theme_classic()+ xlim(-0.3, 0.3) + ylim(-0.3, 0.3)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T3.pdf")
```

Ordination plots rarefied
```{r}
ord_t1_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T1"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T1_rare<-ggordiplots::gg_ordiplot(ord = ord_t1_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_rare_plot<-T1_rare$plot + theme_classic() +  xlim(-0.25, 0.25) + ylim(-0.2, 0.25)  + guides(color=guide_legend("Treatment")) + xlab("NMDS 1") + ylab("NMDS 2")
T1_rare_plot
library(cowplot)
my_legend <- get_legend(T1_rare_plot)
library(ggpubr)
as_ggplot(my_legend)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordinationlegend.pdf")
as_ggplot(my_legend)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordinationlegend.eps")
T1_rare_plot<-T1_rare_plot + theme(legend.position = "none")
T1_rare_plot
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T1.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T1.eps")

ord_t2_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T2"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T2_rare<-ggordiplots::gg_ordiplot(ord = ord_t2_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T2")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T2_rare_plot<-T2_rare$plot + theme_classic() + xlim(-0.25, 0.25) + ylim(-0.2, 0.25)+ theme(legend.position = "none")  + xlab("NMDS 1") + ylab("NMDS 2")
T2_rare_plot
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T2.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T2.eps")

#G166SG identified as outlier based on plots with it included. Removed to create plot. 
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G166SG")
ord_t3_rare<-ordinate(physeq = subset_samples(ps_rare, Time=="T3"), method = "NMDS", distance = "bray", k=3, trymax= 100)
T3_rare<-ggordiplots::gg_ordiplot(ord = ord_t3_rare, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T3")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T3_rare_plot<-T3_rare$plot + theme_classic() + xlim(-0.25, 0.3) + ylim(-0.2, 0.25) + theme(legend.position = "none")  + xlab("NMDS 1") + ylab("NMDS 2")
T3_rare_plot
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T3.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_ordination_rare_T3.eps")


#library(ggpubr)
#ggarrange(T1_rare_plot, T2_rare_plot, T3_rare_plot, ncol = 1)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_ordination.pdf", width = 5, height = 10)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_ordination.eps", width = 5, height = 10)
```

CAP ordination plots rarefied - not used
```{#r}
t1_dist <- distance(subset_samples(ps_rare, Time=="T1"), method="bray") #get wUnifrac and save
t1_table<-as.matrix(dist(t1_dist)) #transform wUnifrac index
ord_t1_rare_cap <- capscale(t1_table ~ Herbicide, data.frame(sample_data(subset_samples(ps_rare, Time == "T1"))))
T1_rare<-ggordiplots::gg_ordiplot(ord = ord_t1_rare_cap, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_rare$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T1_cap.pdf")


t2_dist <- distance(subset_samples(ps_rare, Time=="T2"), method="bray") #get wUnifrac and save
t2_table<-as.matrix(dist(t2_dist)) #transform wUnifrac index
ord_t2_rare_cap <- capscale(t2_table ~ Herbicide, data.frame(sample_data(subset_samples(ps_rare, Time == "T2"))))
T2_rare<-ggordiplots::gg_ordiplot(ord = ord_t2_rare_cap, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T2")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T2_rare$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T2_cap.pdf")


#G166SG identified as outlier based on plots with it included. Removed to create plot. 
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G166SG")
t3_dist <- distance(subset_samples(ps_rare, Time=="T3"), method="bray") #get wUnifrac and save
t3_table<-as.matrix(dist(t3_dist)) #transform wUnifrac index
ord_t3_rare_cap <- capscale(t3_table ~ Herbicide, data.frame(sample_data(subset_samples(ps_rare, Time == "T3"))))
T3_rare<-ggordiplots::gg_ordiplot(ord = ord_t3_rare_cap, groups = data.frame(sample_data(subset_samples(ps_rare, Time == "T3")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T3_rare$plot + theme_classic()
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_rare_T3_cap.pdf")
ggplot_build(T3_rare$plot)$data


```


Pairwise adonis testing
```{r}
ps_pairwiseadonis<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
pairwiseAdonis::pairwise.adonis(x = physeq_dist, factors = md_tab$Herbicide, p.adjust.m = "none", perm = 1000)
}

ps_t1<-subset_samples(ps_rare_sub, Time == "T1")
ps_t1<-prune_taxa(taxa_sums(ps_t1) > 2, ps_t1)

ps_t2<-subset_samples(ps_rare_sub, Time == "T2")
ps_t2<-prune_taxa(taxa_sums(ps_t2) > 2, ps_t2)

ps_t3<-subset_samples(ps_rare_sub, Time == "T3")
ps_t3<-prune_taxa(taxa_sums(ps_t3) > 2, ps_t3)


ps_pairwiseadonis(ps_t1)
ps_pairwiseadonis(ps_t2)
ps_pairwiseadonis(ps_t3)
```

Pairwise betadispr by treatment, time and mode
```{r}
ps_betadispr<-function(physeq, groupingvar = "Groupingvar"){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
                mod<-vegan::betadisper(physeq_dist, md_tab[,groupingvar])
        ## Perform test
                print(anova(mod))
        ## Permutation test for F
                pmod <- vegan::permutest(mod, permutations = 1000, pairwise = TRUE)
                print(pmod)
                print(boxplot(mod))
}
```


permute test of disperson 
```{r}
ps_betadispr(subset_samples(ps_rare_sub, Time == "T1"), groupingvar = "Mode")
ps_betadispr(subset_samples(ps_rare_sub, Time == "T2"), groupingvar = "Mode")
ps_betadispr(subset_samples(ps_rare_sub, Time == "T3"), groupingvar = "Mode")


ps_betadispr(subset_samples(ps_rare_sub, Mode == "Chemical"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Mode == "Non-Treated"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Mode == "Hand"), groupingvar = "Time")


ps_betadispr(subset_samples(ps_rare_sub, Time == "T1"), groupingvar = "Herbicide")
ps_betadispr(subset_samples(ps_rare_sub, Time == "T2"), groupingvar = "Herbicide")
ps_betadispr(subset_samples(ps_rare_sub, Time == "T3"), groupingvar = "Herbicide")


ps_betadispr(subset_samples(ps_rare_sub, Herbicide == "Glyphosate"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Herbicide == "Atrazine-Mesotrione"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Herbicide == "Dicamba"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Herbicide == "Handweeded"), groupingvar = "Time")
ps_betadispr(subset_samples(ps_rare_sub, Herbicide == "Non-Treated"), groupingvar = "Time")

ps_betadispr(ps_rare_sub, groupingvar = "Herbicide")
ps_betadispr(ps_rare_sub, groupingvar = "Mode")
ps_betadispr(ps_rare_sub, groupingvar = "Time")
```


```{r}
beta_boxplot<-function (physeq, method = "bray", group) 
{
  require("phyloseq")
  require("ggplot2")
  group2samp <- list()
  group_list <- get_variable(sample_data(physeq), group)
  for (groups in levels(group_list)) {
    target_group <- which(group_list == groups)
    group2samp[[groups]] <- sample_names(physeq)[target_group]
  }
  beta_div_dist <- phyloseq::distance(physeq = physeq, method = method)
  beta_div_dist <- as(beta_div_dist, "matrix")
  dist_df <- data.frame()
  counter <- 1
  for (groups in names(group2samp)) {
    sub_dist <- beta_div_dist[group2samp[[groups]], group2samp[[groups]]]
    no_samp_col <- ncol(sub_dist)
    no_samp_row <- nrow(sub_dist)
    for (cols in seq(no_samp_col)) {
      if (cols > 1) {
        for (rows in seq((cols - 1))) {
          dist_df[counter, "sample_pair"] <- paste0(colnames(sub_dist)[cols], 
            "-", rownames(sub_dist)[rows])
          dist_df[counter, "group"] <- groups
          dist_df[counter, "beta_div_method"] <- method
          dist_df[counter, "beta_div_value"] <- sub_dist[rows, 
            cols]
          counter = counter + 1
        }
      }
    }
  }
  plot_boxplot <- ggplot(data = dist_df, aes(x = group, y = beta_div_value, 
    color = group)) + geom_boxplot(outlier.shape = NA) + 
    geom_jitter() + theme_bw() + xlab(group) + ylab(method) + 
    theme(axis.text.x = element_text(angle = 45, vjust = 1, 
      hjust = 1))
  list_Out <- list(data = dist_df, plot = plot_boxplot)
  return(list_Out)
}

```

box and whisker plots of pairwise distance 
within group distances
```{r}
#remotes::install_github("antonioggsousa/micrUBIfuns")
#library(micrUBIfuns)
T1_beta<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T1"), method = "bray", group = "Herbicide")
T1_beta_plot <- T1_beta$plot
T1_beta_plot <- T1_beta_plot + theme_classic()+ guides(color=guide_legend("Treatment")) + ylab("Bray-Curtis Dissimilarity") + xlab("") + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75)
T1_beta_plot
my_legend <- get_legend(T1_beta_plot)
#as_ggplot(my_legend)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_beta_legend.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_beta_legend.eps")
T1_beta_plot<-T1_beta_plot+ theme(legend.position = "none") 
T1_beta_plot
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T1_rare_withingroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_T1_rare_withingroup_beta.eps")
T1_beta_df<- T1_beta$data
T1_betamod<-aov(formula = beta_div_value ~ group ,data = T1_beta_df)
summary(T1_betamod)
TukeyHSD(x = T1_betamod, which = "group")

T2_beta<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T2"), method = "bray", group = "Herbicide")
T2_beta_plot <- T2_beta$plot
T2_beta_plot <- T2_beta_plot+ theme_classic() + theme(legend.position = "none") + ylab("Bray-Curtis Dissimilarity") + xlab("") + ggtitle("") + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75)
T2_beta_plot
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T2_rare_withingroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_T2_rare_withingroup_beta.eps")
T2_beta_df<- T2_beta$data
T2_betamod<-aov(formula = beta_div_value ~ group ,data = T2_beta_df)
summary(T2_betamod)
TukeyHSD(x = T2_betamod, which = "group")

T3_beta<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T3"), method = "bray", group = "Herbicide") 
T3_beta$plot #+ scale_color_manual(values = c("#F8766D", "#A3A500",  "#00BF7D", "#00B0F6", "#E76BF3")) + 
T3_beta_plot <- T3_beta$plot
T3_beta_plot <- T3_beta_plot + theme_classic()+ theme(legend.position = "none") + ylab("Bray-Curtis Dissimilarity") + xlab("") + ggtitle("")
T3_beta_plot <-T3_beta_plot + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T3_rare_withingroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/Individual Figures/16S_T3_rare_withingroup_beta.eps")

T3_beta_df<- T3_beta$data
T3_betamod<-aov(formula = beta_div_value ~ group ,data = T3_beta_df)
summary(T3_betamod)
TukeyHSD(x = T3_betamod, which = "group")

library(ggpubr)
plot_combined_treatment_beta_disper<-ggarrange(T1_beta_plot, T2_beta_plot, T3_beta_plot, ncol = 3)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_rare_within_group_beta.pdf", width = 5, height = 10)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/CombinedFigures/Supp_figure_16S_combined_rare_within_group_beta.eps", plot_combined_treatment_beta_disper)
```

Examination of dissimliarity across time points by treatment and then again by all chemical treatments combined.
```{r}
T1_beta_df$Time<-"T1"
T2_beta_df$Time<-"T2"
T3_beta_df$Time<-"T3"


beta_div_T1_T2_T3 <- rbind(T1_beta_df, T2_beta_df, T3_beta_df)

beta_anova<-function(data, Herbicide = "Herbicide"){
  df_sub<- data %>% filter(group == Herbicide)
  mod<-aov(beta_div_value ~ Time, data = df_sub)
  print(summary(mod))
  print(TukeyHSD(mod, "Time"))
  boxplot(df_sub$beta_div_value ~ df_sub$Time)
}

beta_anova(beta_div_T1_T2_T3, Herbicide = "Non-Treated")
beta_anova(beta_div_T1_T2_T3, Herbicide = "Handweeded")
beta_anova(beta_div_T1_T2_T3, Herbicide = "Dicamba")
beta_anova(beta_div_T1_T2_T3, Herbicide = "Atrazine-Mesotrione")
beta_anova(beta_div_T1_T2_T3, Herbicide = "Glyphosate")

#regroup all chemical treatments together and rerun betadiv calcs within group. 
sample_data(ps_rare)$Mode<-sample_data(ps_rare)$Herbicide

index <- c("Dicamba", "Glyphosate", "Atrazine-Mesotrione", "Handweeded", "Non-Treated")
values <- c("Chemical", "Chemical", "Chemical", "Handweeded", "Non-Treated")

sample_data(ps_rare)$Mode<- as.factor(values[match(sample_data(ps_rare)$Mode, index)])

#+ scale_color_manual(values = c("#FFA500", "#00B0F6", "#E76BF3")) 


T1_beta_chemical_combined<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T1"), method = "bray", group = "Mode")
T1_beta_chemical_combined_plot <- T1_beta_chemical_combined$plot 
T1_beta_chemical_combined_plot<- T1_beta_chemical_combined_plot + theme_classic() + guides(color=guide_legend("Treatment")) + ylab("Bray-Curtis Dissimilarity") + xlab("") + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75) + scale_color_manual(values = c("#FFA500", "#00B0F6", "#E76BF3")) 
T1_beta_chemical_combined_plot
my_legend <- get_legend(T1_beta_chemical_combined_plot)
as_ggplot(my_legend)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_beta_combined_legend.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Combined Plots/16S_beta_combined_legend.eps")
T1_beta_chemical_combined_plot<-T1_beta_chemical_combined_plot+ theme(legend.position = "none")
T1_beta_chemical_combined_plot
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Combined Plots/T1_beta_chemical_combined_plot.eps")

T2_beta_chemical_combined<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T2"), method = "bray", group = "Mode")
T2_beta_chemical_combined_plot <- T2_beta_chemical_combined$plot 
T2_beta_chemical_combined_plot<- T2_beta_chemical_combined_plot + theme_classic()+ theme(legend.position = "none") + ylab("Bray-Curtis Dissimilarity") + xlab("") + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75) + scale_color_manual(values = c("#FFA500", "#00B0F6", "#E76BF3")) 
T2_beta_chemical_combined_plot
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Combined Plots/T2_beta_chemical_combined_plot.eps")


T3_beta_chemical_combined<-beta_boxplot(physeq = subset_samples(ps_rare, Time=="T3"), method = "bray", group = "Mode")
T3_beta_chemical_combined_plot <- T3_beta_chemical_combined$plot 
T3_beta_chemical_combined_plot<- T3_beta_chemical_combined_plot + theme_classic()+ theme(legend.position = "none") + ylab("Bray-Curtis Dissimilarity") + xlab("") + theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) + ylim (0.5, 0.75) + scale_color_manual(values = c("#FFA500", "#00B0F6", "#E76BF3")) 
T3_beta_chemical_combined_plot
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Combined Plots/T3_beta_chemical_combined_plot.eps")

ggarrange(T1_beta_chemical_combined_plot, T2_beta_chemical_combined_plot, T3_beta_chemical_combined_plot, ncol = 1)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_rare_within_group_beta_chemical_combined.pdf", width = 5, height = 10)
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Combined Plots/16S_combined_rare_within_group_beta_chemical_combined.eps", width = 5, height = 10)


#build combined plot 
T1_beta_chemical_combined$data$Time <- "T1"
T2_beta_chemical_combined$data$Time <- "T2"
T3_beta_chemical_combined$data$Time <- "T3"

datt1 <- T1_beta_chemical_combined$data

datt2 <- T2_beta_chemical_combined$data

datt3<- T3_beta_chemical_combined$data


dat_combined <- rbind(datt1, datt2, datt3)

ggplot(data = dat_combined) + geom_boxplot(aes(x = Time, y = beta_div_value, fill = Time)) + facet_grid(cols = vars(group))

beta_disper_Chemical_treatment_16S <-ggplot() + geom_boxplot(data = dat_combined, aes(x = Time, y = beta_div_value, color = Time)) + 
  geom_smooth(data = dat_combined, aes(x = Time, y = beta_div_value, group=group),  se= F, method = "lm", color = "black") + 
  scale_x_discrete(labels=c("T1" = "Pre-treatment", "T2" = "10 days \npost-treatment", "T3" = "20 days \npost-treatment")) + ylab("Bray-Curtis dissimiliarity") +
    facet_grid(cols = vars(group))  + theme_classic() + theme(strip.text = element_text(size = 20, color = "black"))
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/FinalPlots/betadisper_chemicaltreatment.eps", beta_disper_Chemical_treatment_16S, height = 4, width = 10, dpi = 600)

```

```{r}
T1_beta_df_chemical_combined <- T1_beta_chemical_combined$data
T2_beta_df_chemical_combined<- T2_beta_chemical_combined$data
T3_beta_df_chemical_combined<- T3_beta_chemical_combined$data

T1_beta_df_chemical_combined$Time<-"T1"
T2_beta_df_chemical_combined$Time<-"T2"
T3_beta_df_chemical_combined$Time<-"T3"

m1<-aov(beta_div_value ~ group, data = T1_beta_df_chemical_combined)
summary(m1)
TukeyHSD(m1, "group")
boxplot(beta_div_value ~ group, data = T1_beta_df_chemical_combined)


m2<-aov(beta_div_value ~ group, data = T2_beta_df_chemical_combined)
summary(m2)
TukeyHSD(m2, "group")
boxplot(beta_div_value ~ group, data = T2_beta_df_chemical_combined)

m3<-aov(beta_div_value ~ group, data = T3_beta_df_chemical_combined)
summary(m3)
TukeyHSD(m3, "group")
boxplot(beta_div_value ~ group, data = T3_beta_df_chemical_combined)


beta_div_chemical_combined_T1_T2_T3 <- rbind(T1_beta_df_chemical_combined, T2_beta_df_chemical_combined, T3_beta_df_chemical_combined)

beta_anova(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Chemical")
beta_anova(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Handweeded")
beta_anova(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Non-Treated")

beta_lm<-function(data, Herbicide = "Herbicide"){
  df_sub<- data %>% filter(group == Herbicide)
  mod<-lm(beta_div_value ~ Time, data = df_sub)
  print(summary(mod))
  print(coef(mod))
  #print(TukeyHSD(mod, "Time"))
  #boxplot(df_sub$beta_div_value ~ df_sub$Time)
}

beta_div_chemical_combined_T1_T2_T3$Time <- replace(beta_div_chemical_combined_T1_T2_T3$Time, beta_div_chemical_combined_T1_T2_T3$Time== "T1", 0)
beta_div_chemical_combined_T1_T2_T3$Time <- replace(beta_div_chemical_combined_T1_T2_T3$Time, beta_div_chemical_combined_T1_T2_T3$Time== "T2", 10)
beta_div_chemical_combined_T1_T2_T3$Time <- replace(beta_div_chemical_combined_T1_T2_T3$Time, beta_div_chemical_combined_T1_T2_T3$Time== "T3", 20)

beta_div_chemical_combined_T1_T2_T3$Time <- as.numeric(beta_div_chemical_combined_T1_T2_T3$Time)

beta_lm(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Chemical")
beta_lm(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Handweeded")
beta_lm(beta_div_chemical_combined_T1_T2_T3, Herbicide = "Non-Treated")
```

treatment to control 
```{r}
plotDistances = function(p, m, s, d) {

  # calc distances
  wu = phyloseq::distance(p, m)
  wu.m = melt(as.matrix(wu))
  
  # remove self-comparisons
  wu.m = wu.m %>%
    filter(as.character(Var1) != as.character(Var2)) %>%
    mutate_if(is.factor,as.character)
  
  # get sample data (S4 error OK and expected)
  sd = data.frame(sample_data(p)) %>%
    select(s, d) %>%
    mutate_if(is.factor,as.character)
  sd$Herbicide <- factor(sd$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
  
  # combined distances with sample data
  colnames(sd) = c("Var1", "Type1")
  wu.sd = left_join(wu.m, sd, by = "Var1")
  
  colnames(sd) = c("Var2", "Type2")
  wu.sd = left_join(wu.sd, sd, by = "Var2")
  
  #remove this line to plot all comparisons. 
  #wu.sd = wu.sd %>% filter(Type1 == "Hand" | Type1 == "Non-Treated")
  
  # plot
  ggplot(wu.sd, aes(x = Type2, y = value)) +
    theme_bw() +
    geom_point() +
    geom_boxplot(aes(color = ifelse(Type1 == Type2, "red", "black"))) +
    scale_color_identity() +
    facet_wrap(~ Type1, scales = "free_x") +
    theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
    ggtitle(paste0("Distance Metric = ", m))
  
}
```


```{r}
a<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T1"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
a <- a + ggtitle("Time 1 Bray-Curtis Dissimlarities")
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T1_rare_allgroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T1_rare_allgroup_beta_multicomparison.pdf")
b<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T2"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
b <-b + ggtitle("Time 2 Bray-Curtis Dissimlarities")
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T2_rare_allgroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T2_rare_allgroup_beta_multicomparison.pdf")
c<-plotDistances(p = subset_samples(physeq= ps_rare, Time=="T3"), m = "bray", s = "Barcode_ID_G", d = "Herbicide")
c<- c + ggtitle("Time 3 Bray-Curtis Dissimlarities")
#ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T3_rare_allgroup_beta.pdf")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_T3_rare_allgroup_beta_multicomparison.pdf")

library(ggpubr)
ggarrange(a, b, c, ncol = 1)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_combined_rare_allgroup_beta_multi_comparison.pdf", width = 7, height = 10)
```
Taxon abundance bar plot

```{r}
#create super long color vector
col_vector <- c("#000000", "#FFFF00", "#1CE6FF", "#FF34FF", "#FF4A46", "#008941", "#006FA6", "#A30059",
        "#FFDBE5", "#7A4900", "#0000A6", "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87",
        "#5A0007", "#809693", "#FEFFE6", "#1B4400", "#4FC601", "#3B5DFF", "#4A3B53", "#FF2F80",
        "#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92", "#FF90C9", "#B903AA", "#D16100",
        "#DDEFFF", "#000035", "#7B4F4B", "#A1C299", "#300018", "#0AA6D8", "#013349", "#00846F",
        "#372101", "#FFB500", "#C2FFED", "#A079BF", "#CC0744", "#C0B9B2", "#C2FF99", "#001E09",
        "#00489C", "#6F0062", "#0CBD66", "#EEC3FF", "#456D75", "#B77B68", "#7A87A1", "#788D66",
        "#885578", "#FAD09F", "#FF8A9A", "#D157A0", "#BEC459", "#456648", "#0086ED", "#886F4C",
        
        "#34362D", "#B4A8BD", "#00A6AA", "#452C2C", "#636375", "#A3C8C9", "#FF913F", "#938A81",
        "#575329", "#00FECF", "#B05B6F", "#8CD0FF", "#3B9700", "#04F757", "#C8A1A1", "#1E6E00",
        "#7900D7", "#A77500", "#6367A9", "#A05837", "#6B002C", "#772600", "#D790FF", "#9B9700",
        "#549E79", "#FFF69F", "#201625", "#72418F", "#BC23FF", "#99ADC0", "#3A2465", "#922329",
        "#5B4534", "#FDE8DC", "#404E55", "#0089A3", "#CB7E98", "#A4E804", "#324E72", "#6A3A4C",
        "#83AB58", "#001C1E", "#D1F7CE", "#004B28", "#C8D0F6", "#A3A489", "#806C66", "#222800",
        "#BF5650", "#E83000", "#66796D", "#DA007C", "#FF1A59", "#8ADBB4", "#1E0200", "#5B4E51",
        "#C895C5", "#320033", "#FF6832", "#66E1D3", "#CFCDAC", "#D0AC94", "#7ED379", "#012C58",
        
        "#7A7BFF", "#D68E01", "#353339", "#78AFA1", "#FEB2C6", "#75797C", "#837393", "#943A4D",
        "#B5F4FF", "#D2DCD5", "#9556BD", "#6A714A", "#001325", "#02525F", "#0AA3F7", "#E98176",
        "#DBD5DD", "#5EBCD1", "#3D4F44", "#7E6405", "#02684E", "#962B75", "#8D8546", "#9695C5",
        "#E773CE", "#D86A78", "#3E89BE", "#CA834E", "#518A87", "#5B113C", "#55813B", "#E704C4",
        "#00005F", "#A97399", "#4B8160", "#59738A", "#FF5DA7", "#F7C9BF", "#643127", "#513A01",
        "#6B94AA", "#51A058", "#A45B02", "#1D1702", "#E20027", "#E7AB63", "#4C6001", "#9C6966",
        "#64547B", "#97979E", "#006A66", "#391406", "#F4D749", "#0045D2", "#006C31", "#DDB6D0",
        "#7C6571", "#9FB2A4", "#00D891", "#15A08A", "#BC65E9", "#FFFFFE", "#C6DC99", "#203B3C",

        "#671190", "#6B3A64", "#F5E1FF", "#FFA0F2", "#CCAA35", "#374527", "#8BB400", "#797868",
        "#C6005A", "#3B000A", "#C86240", "#29607C", "#402334", "#7D5A44", "#CCB87C", "#B88183",
        "#AA5199", "#B5D6C3", "#A38469", "#9F94F0", "#A74571", "#B894A6", "#71BB8C", "#00B433",
        "#789EC9", "#6D80BA", "#953F00", "#5EFF03", "#E4FFFC", "#1BE177", "#BCB1E5", "#76912F",
        "#003109", "#0060CD", "#D20096", "#895563", "#29201D", "#5B3213", "#A76F42", "#89412E",
        "#1A3A2A", "#494B5A", "#A88C85", "#F4ABAA", "#A3F3AB", "#00C6C8", "#EA8B66", "#958A9F",
        "#BDC9D2", "#9FA064", "#BE4700", "#658188", "#83A485", "#453C23", "#47675D", "#3A3F00",
        "#061203", "#DFFB71", "#868E7E", "#98D058", "#6C8F7D", "#D7BFC2", "#3C3E6E", "#D83D66",

        "#2F5D9B", "#6C5E46", "#D25B88", "#5B656C", "#00B57F", "#545C46", "#866097", "#365D25",
        "#252F99", "#00CCFF", "#674E60", "#FC009C", "#92896B")
```

```{r}
phylumGlommed <- tax_glom(ps_rare, "Phylum")

#t1
phylumGlommed_herb_t1 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T1"), group = "Herbicide")
phylumGlommed_herb_t1 <- transform_sample_counts(phylumGlommed_herb_t1, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t1)$Herbicide <- factor(sample_data(phylumGlommed_herb_t1)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t1, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_Taxon_barplot_t1.pdf")

#t2
phylumGlommed_herb_t2 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T2"), group = "Herbicide")
phylumGlommed_herb_t2 <- transform_sample_counts(phylumGlommed_herb_t2, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t2)$Herbicide <- factor(sample_data(phylumGlommed_herb_t2)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t2, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_Pt1/Figures/16S_Taxon_barplot_t2.pdf")

#t3
phylumGlommed_herb_t3 <- merge_samples(subset_samples(physeq= phylumGlommed, Time=="T3"), group = "Herbicide")
phylumGlommed_herb_t3 <- transform_sample_counts(phylumGlommed_herb_t3, function(OTU) OTU/sum(OTU))
sample_data(phylumGlommed_herb_t3)$Herbicide <- factor(sample_data(phylumGlommed_herb_t3)$Herbicide, levels = c(1, 2, 3, 4, 5), 
       labels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))

plot_bar(phylumGlommed_herb_t3, x = "Herbicide", fill = "Phylum")  + theme_classic() + ggtitle("Proportional Taxon Abundances Time 1") +
theme(legend.position="bottom") + guides(fill=guide_legend(nrow=6)) + geom_bar(stat="identity") + theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 5)) + 
scale_fill_manual(values = col_vector)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_Pt1/Figures/16S_Taxon_barplot_t3.pdf")
```
Combined herbicide and time bar plot for exploration
```{r}
sample_data(ps_rare)$herb_time<-paste(sample_data(ps_rare)$Herbicide, sample_data(ps_rare)$Time, sep = "_")
ps_rare_for_barplot <- prune_taxa(taxa_sums(ps_rare) > 50, ps_rare)
plot_bar(ps_rare_for_barplot, x= "herb_time", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_BarPlot_Herbicide_Time.pdf", width = 20, height = 11)
```


Linear modeling of abundant taxa. 
```{r}

Tax_glom_Subset <- function (physeq, y = "taxLevel", nreturns = "Number of returns"){
   ps_1<- tax_glom(ps_rare_sub, taxrank = y )
    myTaxa <- names(sort(taxa_sums(ps_1), decreasing = TRUE)[1:nreturns])
       ps_1_sub <- prune_taxa(myTaxa, ps_1)
  return(ps_1_sub)
}


ps_rare_family_top25<-Tax_glom_Subset(physeq = ps_rare, nreturns = 25, y = "Family")

myTaxa <- names(sort(taxa_sums(ps_rare), decreasing = TRUE)[1:25])
ps_rare_asv_top25 <- prune_taxa(myTaxa, ps_rare)


#explore top 25 taxa with plot bar
plot_bar(ps_rare_family_top25, x= "herb_time", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")
plot_bar(ps_rare_family_top25, x= "Time", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")
plot_bar(ps_rare_family_top25, x= "Herbicide", fill = "Family") + scale_fill_manual(values = col_vector) + geom_bar(stat="identity")


#write function to wrangle data prior to anova

abund_aov_wrangle <- function (physeq, y = "Tax_Level"){
  tax<-tax_table(physeq)[,y]
   meta<-data.frame(sample_data(physeq))
  counts<-data.frame(otu_table(physeq))
  rownames(counts) <- tax[,1]
  counts<-data.frame(t(counts))
   counts$Time <- meta$Time 
   counts$Herbicide <- meta$Herbicide 
  counts$Herb_time <- meta$herb_time 
  return(counts)
}            

test<-abund_aov_wrangle(ps_rare_family_top25, y = "Family")



mod_abund<-function(count_tab, IV = "Groups to be tested") {
   for(j in 1:length(unique(count_tab[,"Herbicide"]))){
         data <- count_tab %>% filter(Herbicide == unique(count_tab$Herbicide)[j])
           #change this to the number of returns from the tax_glom_subset function
   for (i in 1:25) { 
            mod <- aov(unlist(data[i]) ~ matrix(data[,IV])) 
            #sanity check
            #print(c(j, i))
   if(summary(mod)[[1]][["Pr(>F)"]][1] <= 0.05) {
            #print(summary(mod))
     print(c(as.character(unique(count_tab[,"Herbicide"]))[j], names(data)[i]))
              boxplot(unlist(data[i]) ~ unlist(data[IV]), main =paste(names(data[i]), as.character(unique(count_tab[,"Herbicide"]))[j]), xlab= "Time", ylab="Abundance") 
           }
         }
      }
    }


mod_abund(test, IV = "Time")
```
