---
title: "HerbPt1 16S Figures"
output: html_notebook
---

```{r}
require(phyloseq)
require(tidyverse)
```

Load data
```{r}
ps_dmn <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/DMN_ests_16S.Rdata")
sample_data(ps_dmn)$Herbicide <- factor(sample_data(ps_dmn)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
ps_rare <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_rare_16S.Rdata")
sample_data(ps_rare)$Herbicide <- factor(sample_data(ps_rare)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
ps_trans <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/16S/HerbPt1_hel_trans_16S.Rdata")
sample_data(ps_trans)$Herbicide <- factor(sample_data(ps_trans)$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
```

create alphadiversity tables
```{r}
alpha_div <- estimate_richness(physeq = ps_rare, measures = c("Observed", "Shannon", "Chao1"))
#pull out metadata and concatonate with alpha diversity metrics
md<-data.frame(sample_data(ps_rare))
alpha_div_md <- rownames_to_column(alpha_div, "Barcode_ID_G") %>% full_join(md) 
alpha_div_md$Herbicide <- factor(alpha_div_md$Herbicide, levels = c("Non-Treated", "Hand", "Aatrex", "Clarity", "Roundup Powermax"))
```

Shannon Div plots - no significant differences among herbicide treatments at any of the three time points
```{r}
ggplot(data = alpha_div_md, aes(Herbicide, Shannon, color= Herbicide)) + facet_grid(. ~ Time) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 45, hjust = 1) )

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_Shannon.pdf")

aov_t1<-aov(Shannon ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T1",])
plot(aov_t1$residuals)
summary(aov_t1)

aov_t2<-aov(Shannon ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T2",])
plot(aov_t2$residuals)
summary(aov_t2)

aov_t3<-aov(Shannon ~ Herbicide, data = alpha_div_md[alpha_div_md$Time == "T3",])
plot(aov_t3$residuals)
summary(aov_t3)
```

ordinations and adonis testing with three separate objects (i.e., dmn, rarefied, transformed). Rare taxa are removed from rarefied and transfomred to sucessfully ordinate. At this point, the transformed data will not ordinate. 
```{r}
ord_dmn<-ordinate(physeq = ps_dmn, method = "NMDS", distance = "bray", k=3, trymax= 100)

ps_rare_sub<-prune_taxa(taxa_sums(ps_rare) > 2, ps_rare)
ord_rare<-ordinate(physeq = ps_rare_sub, method = "NMDS", distance = "bray", k=3, trymax= 100, previous.best = ord_rare)

#can't get the hellinger transformed data to ordinate successfully
ps_trans_sub<-prune_taxa(taxa_sums(ps_trans) > 0.5, ps_trans)
ord_transformed<-ordinate(physeq = ps_trans_sub, method = "NMDS", distance = "bray", k=3, trymax= 100)
```

Adonis testing of herbicide treatments by time point
```{r}
ps_adonis<-function(physeq){
  otu_tab<-data.frame(phyloseq::otu_table(physeq))
  md_tab<-data.frame(phyloseq::sample_data(physeq))
    if(taxa_are_rows(physeq)== T){
       physeq_dist<-parallelDist::parDist(as.matrix(t(otu_tab)), method = "bray")}
            else{physeq_dist<-parallelDist::parDist(as.matrix(otu_tab), method = "bray")}
  print(anova(vegan::betadisper(physeq_dist, md_tab$Herbicide)))
  vegan::adonis(physeq_dist ~ Herbicide * Time, data = md_tab)
}
```

```{r}
ps_adonis(ps_rare_sub)
ps_adonis(ps_trans_sub)
ps_adonis(ps_dmn)
```

Ordination plots DMN
```{r}
ord_t1_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T1"), method = "NMDS", distance = "bray", k=3, trymax= 100)
plot_ordination(physeq = subset_samples(ps_dmn, Time=="T1"), ordination = ord_t1_dmn, type = "Samples", axes = c(1,2), color = "Herbicide") +  theme_classic() +  stat_ellipse(type = "norm", linetype = 2, level = 0.95) 

T1_dmn<-ggordiplots::gg_ordiplot(ord = ord_t1_dmn, groups = data.frame(sample_data(subset_samples(ps_dmn, Time == "T1")))$Herbicide, choices = c(1, 2), kind = c("se"), conf = 0.95, show.groups = "all", ellipse = TRUE, label = FALSE, hull = FALSE, spiders = FALSE, plot = TRUE, pt.size = 1)
T1_dmn$plot + theme_classic()

ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T1.pdf")

ord_t2_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T2"), method = "NMDS", distance = "bray", k=3, trymax= 100)
plot_ordination(physeq = subset_samples(ps_dmn, Time=="T2"), ordination = ord_t2_dmn, type = "Samples", axes = c(1,2), color = "Herbicide") +  theme_classic() + stat_ellipse(type = "norm", linetype = 2)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T2.pdf")


ord_t3_dmn<-ordinate(physeq = subset_samples(ps_dmn, Time=="T3"), method = "NMDS", distance = "bray", k=3, trymax= 100)
plot_ordination(physeq = subset_samples(ps_dmn, Time=="T3"), ordination = ord_t3_dmn, type = "Samples", axes = c(1,2), color = "Herbicide") +  theme_classic() + stat_ellipse(type = "norm", linetype = 2)
ggsave("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/16S_ordination_dmn_T3.pdf")


ord_rare<-ordinate(physeq = ps_rare_sub, method = "NMDS", distance = "bray", k=3, trymax= 100)

#can't get the hellinger transformed data to ordinate successfully
ps_trans_sub<-prune_taxa(taxa_sums(ps_trans) > 0.5, ps_trans)
ord_transformed<-ordinate(physeq = ps_trans_sub, method = "NMDS", distance = "bray", k=3, trymax= 100)
```

