---
title: "Important Taxa with Boruta algo ITS"
output: html_notebook
---


```{r}
library(randomForest)
library(Boruta)
library(phyloseq)
library(stats)
library(dplyr)
library(readr)
library(pheatmap)
library(tidyverse)
```

read in rarefied data
```{r}
ps_rare <- readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/ITS/HerbPt1_rare_ITS.Rdata")
sample_data(ps_rare)$Herbicide <- factor(sample_data(ps_rare)$Herbicide, levels = c("Aatrex", "Clarity", "Hand","Non-Treated","Roundup Powermax"))
sample_data(ps_rare)$herb_time<-paste(sample_data(ps_rare)$Herbicide, sample_data(ps_rare)$Time, sep = "_")

#remove outlier samples and prune rare taxa
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G009SG")
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G095SG")
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G123SG")
ps_rare <-  subset_samples(ps_rare, sample_names(ps_rare) != "G129SG")
ps_rare_abund<-prune_taxa(taxa_sums(ps_rare) > 2, ps_rare)
```
split by time point
```{r}
ps_rare1 <- subset_samples(ps_rare_abund, Time == "T1")
ps_rare2 <- subset_samples(ps_rare_abund, Time == "T2")
ps_rare3 <- subset_samples(ps_rare_abund, Time == "T3")
```


Function for phylsoeq object. This can likely be cleaned up significantly. Theres some extra steps for sure. I more or less just took it from the plotting script and went from there. Full plotting script can be found below (2-4-22, gc.) 
```{r}
baruta_phyloseq<-function(physeq = "Phyloseq object", GroupingVar = "Grouping variable"){
  #prep data
  df <- data.frame(t(otu_table(physeq)))
  md <- data.frame(sample_data(physeq))
  tax <- data.frame(tax_table(physeq))
  rownames(tax)<-str_replace(rownames(tax), pattern = "[[.]]", replacement = "=")
  #run simper
 
                  boruta_layer <- Boruta(df , factor(md[,GroupingVar]), 
                      doTrace = 1, ntree = 1000, maxRuns = 1000) # adjust factor!!!!

                  B1 <- data.frame(boruta_layer$finalDecision)  
                  B2 <- data.frame(apply(boruta_layer$ImpHistory, 2, mean))
                  names(B1) <- "Layer_decision"
                  names(B2) <- "Layer_importance"
                  BB1 <- merge(B1, B2, by="row.names", all.x=TRUE)
                  #sorting the results
                  BB1_sort <- BB1[order(BB1$Layer_importance, decreasing = TRUE),] ## this is to give an overwiew and choose cutoff
                  #picking up important with cutoff
                  BB1_sort_cutoff <- filter(BB1, Layer_importance >= 2) ## number is your importance cutoff

                        #picking up OTUs from full otutable
                        signOTU <- as.matrix(BB1_sort_cutoff$Row.names) #vector with OTUs
                        signOTU<-str_replace(signOTU, pattern = "[[.]]", replacement = ".")
                        #my_taxa
                        tax$OTU <-rownames(tax)
                        signOTU<-str_replace(signOTU, pattern = "[[.]]", replacement = "=")
                        signmy_taxa <- filter(tax, OTU %in% signOTU) 
                        signmy_taxa <- as.data.frame(signmy_taxa)
                        taxa_keep<-signmy_taxa$OTU
return(taxa_keep)
}

```


```{r}
baruta_t1_taxa<-baruta_phyloseq(ps_rare1, GroupingVar = "Herbicide")
baruta_t2_taxa<-baruta_phyloseq(ps_rare2, GroupingVar = "Herbicide")
baruta_t3_taxa<-baruta_phyloseq(ps_rare3, GroupingVar = "Herbicide")
```



```{r}
ps_baruta_t1 <- subset_taxa(ps_rare_abund, taxa_names(ps_rare_abund) %in% baruta_t1_taxa)
ps_baruta_t2 <- subset_taxa(ps_rare_abund, taxa_names(ps_rare_abund) %in% baruta_t2_taxa)
ps_baruta_t3 <- subset_taxa(ps_rare_abund, taxa_names(ps_rare_abund) %in% baruta_t3_taxa)

merged_baruta<-merge_phyloseq(ps_baruta_t1, ps_baruta_t2, ps_baruta_t3)
```


```{r}
saveRDS(merged_baruta, "/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/ITS/Baruta_taxa_ITS_rareified.Rdata")
```




Merge phyloseq objects for Linera modeling efforts by Josh
```{r}
#clean env but keep merged Baruta object. Read in Simper object
merged_simper<-readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/ITS/Simper_taxa_ITS_rareified.Rdata")
merged_baruta<-readRDS("/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/ITS/Baruta_taxa_ITS_rareified.Rdata")
```

```{r}
merged_baruta_simper <- merge_phyloseq(merged_baruta, merged_simper)
saveRDS(merged_baruta_simper, "/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/data/PhyloseqObjects/ITS/merged_simper_baruta_ITS.Rdata")
```




```{r}
rowSums(data.frame(otu_table(merged_baruta_simper)))


merged_baruta_simper_herb_time <- merge_samples(merged_baruta_simper, group = "herb_time")
micrUBIfuns::plot_taxa_heatmap(merged_baruta_simper_herb_time, rm_na = T, scale_by = "taxa",annot_samples = "herb_time", cluster_rows=F, cluster_columns = T)


merged_baruta_simper_herb<- merge_samples(merged_baruta_simper, group = "Herbicide")
micrUBIfuns::plot_taxa_heatmap(merged_baruta_simper_herb, rm_na = T, scale_by = "taxa",annot_samples = "Herbicide", cluster_rows=F, cluster_columns = T)

merged_baruta_simper_time<- merge_samples(merged_baruta_simper, group = "Time")
micrUBIfuns::plot_taxa_heatmap(merged_baruta_simper_time, rm_na = T, scale_by = "taxa", annot_samples = "Time", cluster_rows=F, cluster_columns = T)
```








Full plotting script below. 
Used to test initial walk through. Not being used now. Might revist if we decide to make heatmaps.
```{r}
#shitty switch 
ps<-ps_rare3

df <- data.frame(t(otu_table(ps)))
md <- data.frame(sample_data(ps))
tax <- data.frame(tax_table(ps))
rownames(tax)<-str_replace(rownames(tax), pattern = "[[.]]", replacement = "=")
```

# Running Boruta, testing for variables that are differentially distributed 
# among the two layers (That is why I used my_factors$Layer). If you want to run the analysis
# with the other factor use "my_factors$Treatment" instead.
```{r}
boruta_layer <- Boruta(df , factor(md$Herbicide), 
                      doTrace = 1, ntree = 1000, maxRuns = 1000) # adjust factor!!!!
```

```{r}
# The boruta_layer object has different results inside.
# You can extract the results using the following lines of code

# To extract a table with the decisions 
B1 <- data.frame(boruta_layer$finalDecision)  
```

```{r}
# To extract a table with the decisions, a number that tells you how likely is that 
# your variable is a significant predictor. The $ImpHistory results will 
# tell you the score for each round that Random forests use, here I am reporting the average 
# for all the rounds. The ones that are very low and non-significant will appear as -inf
# So do not worry about those
B2 <- data.frame(apply(boruta_layer$ImpHistory, 2, mean))

# Then I change the names in the table , join them together and export the 
# results as another .csv file which can be opened in excel

names(B1) <- "Layer_decision"
names(B2) <- "Layer_importance"
BB1 <- merge(B1, B2, by="row.names", all.x=TRUE)
```


```{r}
#sorting the results
BB1_sort <- BB1[order(BB1$Layer_importance, decreasing = TRUE),] ## this is to give an overwiew and choose cutoff
#picking up important with cutoff
BB1_sort_cutoff <- filter(BB1, Layer_importance >= 2) ## number is your importance cutoff

#picking up OTUs from full otutable
signOTU <- as.matrix(BB1_sort_cutoff$Row.names) #vector with OTUs
signOTU<-str_replace(signOTU, pattern = "[[.]]", replacement = ".")
tmy_data <- as.data.frame(cbind(row.names(t(df)),t(df))) #data cosmetics - transposition , rownames to col, dataframe
signOTUtable <- filter(tmy_data, V1 %in% signOTU) # there is automatically generated colname it can be problematic
rownames(signOTUtable) <- signOTUtable[,1]#data cosmetics
signOTUtable <- signOTUtable[,-1]#data cosmetics
signOTUtable_rnames<-rownames(signOTUtable)
str(signOTUtable)
signOTUtable<-as.data.frame(lapply(signOTUtable, as.numeric))
rownames(signOTUtable)<-signOTUtable_rnames
str(signOTUtable)
#z-score
signOTU_scale <- scale(t(signOTUtable), center = TRUE, scale = TRUE) #calculating z-score
signOTU_scale <- as.data.frame(t(signOTU_scale)) #data cosmetics 


```

ready taxa for heatmap
```{r}
#my_taxa
tax$OTU <-rownames(tax)

#my_taxa = (read.csv("OC_taxtable.csv", header=TRUE, row.names=1))
#my_taxa <- as.data.frame(cbind(row.names(my_taxa),(my_taxa))) #data cosmetics
#colnames(my_taxa) <- c("OTU","Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")

signOTU<-str_replace(signOTU, pattern = "[[.]]", replacement = "=")
signmy_taxa <- filter(tax, OTU %in% signOTU) 
```







Explore plotting options
```{r}
ordered_data<-data.frame(t(signOTU_scale))
ordered_data$Herbicide <- md$Herbicide
ordered_data <- ordered_data[order(ordered_data$Herbicide),]
ordered_data$Herbicide = NULL
sorted_sign_otu_scale<-data.frame(t(ordered_data))  
rownames(sorted_sign_otu_scale) <- paste(signmy_taxa$OTU, signmy_taxa$Kingdom, signmy_taxa$Phylum, signmy_taxa$Class, signmy_taxa$Order, signmy_taxa$Family, signmy_taxa$Genus, signmy_taxa$Species, sep = ";")
Bac.factorsDS <- select(md, Herbicide)

#HMP1<-pheatmap(sorted_sign_otu_scale, cluster_rows = TRUE, cluster_cols = FALSE, scale = "row", cellwidth = 10, cellheigh = 10, fontsize = 10, color = colorRampPalette(c("blue", "white", "red"))(11), annotation_col = Bac.factorsDS)

#HMP2<-pheatmap(sorted_sign_otu_scale, cluster_rows = TRUE, cluster_cols = FALSE, scale = "row", cellwidth = 10, cellheigh = 10, fontsize = 10, color = colorRampPalette(c("blue", "white", "red"))(11), annotation_col = Bac.factorsDS)


HMP3<-pheatmap(sorted_sign_otu_scale, cluster_rows = TRUE, cluster_cols = FALSE, scale = "row", cellwidth = 10, cellheigh = 10, fontsize = 10, color = colorRampPalette(c("blue", "white", "red"))(11), annotation_col = Bac.factorsDS)


save_pheatmap_pdf <- function(x, filename, width=30, height=10) {
   stopifnot(!missing(x))
   stopifnot(!missing(filename))
   pdf(filename, width=width, height=height)
   grid::grid.newpage()
   grid::grid.draw(x$gtable)
   dev.off()
}


save_pheatmap_pdf(HMP1, "/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Time1_RF_Taxa.pdf")
save_pheatmap_pdf(HMP2, "/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Time2_RF_Taxa.pdf")
save_pheatmap_pdf(HMP3, "/Users/gordoncuster/Desktop/Git_Projects/Herbicide_Microbes_PT1/Figures/Time3_RF_Taxa.pdf")

```


