---
title: "Fungild Assignments"
output: html_notebook
---

Using the funguildR package:
https://rdrr.io/github/brendanf/FUNGuildR/

Install for inital use
```{#r}
install.packages("remotes")
remotes::install_github("brendanf/FUNGuildR")
```

```{r}
library(FUNGuildR)
library(phyloseq)
library(tidyverse)
```

load ITS time point phyloseq object of interest
```{r}
Time1<-readRDS("../data/Time1_ITS.HMC.rda")
Time2<-readRDS("../data/Time2_ITS.HMC.rda")
Time3<-readRDS("../data/Time3_ITS.HMC.rda")
```

Extract and format taxonomy table and sample data
```{r}
#this function is written assuming there is 2 characters before the meaninfgul infomraiton in the taxonomy string (e.g. "K:Fungi")
#input is your taxonomy table with individual columns for each level of taxonomy
extractandMerge<-function(x){
  x<-data.frame(phyloseq::tax_table(x))
  x$Taxonomy<-paste(substring(x$Kingdom, 3, 1000), substring(x$Phylum, 3, 1000), substring(x$Class, 3, 1000), substring(x$Order, 3, 1000), substring(x$Family, 3, 1000), substring(x$Genus, 3, 1000), substring(x$Species, 3, 1000), sep = ";")
  
  return(x)
}

md_extract<-function(x){
  meta_data<-data.frame(sample_data(x))
  return(meta_data)
}

```

Combine taxonomy and count data. Then assign FunGuild data
```{r}
#inputs phyloseq object
fgAssign<-function(z){
    y<-extractandMerge(z)  
        count_tab<-data.frame(phyloseq::otu_table(z))
  if(table(rownames(count_tab)== rownames(y))){
        count_tab$Centroid<-rownames(count_tab)
           y$Centroid<-rownames(y)
             Tax_count_FG<-dplyr::left_join(count_tab, y, "Centroid")
                p<-FUNGuildR::funguild_assign(Tax_count_FG, db = get_funguild_db(), tax_col = "Taxonomy")
  }
  
    return(p)
}

```

Assign FUNGuild assignemnts
```{r}
T1_FG_Assignments<-fgAssign(Time1)
T2_FG_Assignments<-fgAssign(Time2)
T3_FG_Assignments<-fgAssign(Time3)
```

Query based upon trait, guild, trohpic mode of interest. This example queries any symbiotrophs and mycorrhizae. This top line queried against the output of the fgAssign and the bottomthe entire database not your output. 
```{r}
symbiotrophs <- funguild_query("*Symbiotroph*", "trophicMode", db = T1_FG_Assignments)
mycorrhizae <- funguild_query("*Mycorrhizal*", "guild")
```
Convert query output to correct format. This can be done for any of the inputs from the above query step. 
```{r}
trophic_modes<- symbiotrophs %>% filter(confidenceRanking == "Highly Probable" | confidenceRanking == "Probable") %>% select(starts_with(c("G0", "G1", "trophicMode"))) %>% group_by(trophicMode) %>% summarise(across(where(is.numeric), mean)) %>% column_to_rownames("trophicMode") %>%  t() %>% data.frame() %>% rownames_to_column("Barcode")
```
extract metadata
```{r}
T1_md<-md_extract(Time1)
T2_md<-md_extract(Time2)
T3_md<-md_extract(Time3)
```


Combine metadata and count/FG table
```{r}
md_sd_fg_t1<-left_join(T1_md, trophic_modes, by = c("Barcode_ID_G" = "Barcode"))
md_sd_fg_t2<-left_join(T2_md, trophic_modes, by = c("Barcode_ID_G" = "Barcode"))
md_sd_fg_t3<-left_join(T3_md, trophic_modes, by = c("Barcode_ID_G" = "Barcode"))
```

 summary(aov(Symbiotroph ~ Herbicide, data = md_sd_fg))